The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
coefficients and ppc results

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A\\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\
        \\ \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope One Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
        \\
        \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
     \textbf{Model 5} & ${\textrm{Yield} \times \textrm{Average Sale Price}}\over{\textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year * Region\end{tabular}
        \end{tabular}}
\end{table}

@@

Predictor variables used in this analysis included yield, defined as the total tonnes of grapes harvested, and quality, defined as the average sale price. It is acknowledged that quality can be defined in a variety of ways, for example by the grapes': aroma, chemical composition and color \citep{kasimatiPredictingGrapeSugar2022,mejeanperrotDecisionsupportSystemPredict2022,suarezAssessingWineGrape2021}. Using sale price was based on the reliance of market value of winegrapes on grape quality and because Wine Australia explicitly defines grape quality through the use of discrete price brackets in their annual reports. The generalisation made to reflect quality through using average price assumed a due diligence of those who purchased the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

Missing values were improved using regional average prices from Wine Australia. Two subsets of data were then created for the analysis. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table \ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for two further models (Models 3 and 4, see Table \ref{tab:tab1}. These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table \ref{tab:tab1}), where every sample had a recorded value for yield but not average price of sale per tonne.

@@

\newline
%%
%%
%%
% This is where the maps go!
%%
%%
%%

@@

\subsection{Exploratory Analysis} \label{sec:exp_anal}
 Table \ref{tab:summary} shows the summary statistics of each variable used in Models 1 to 4 (See \ref{tab:tab1}).

@@

      \resizebox{\textwidth}{!}{

@@

          {Yield} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\

@@

          {Area Harvested} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\

@@

          {Water Used} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\

@@

          {Scope One Emissions} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\

@@

          ${Yield}\over \textbf{Area}$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\

@@

          {Average Sale Price} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\

@@

          ${Average Sale Price} \over \textbf{Area Harvested}$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule

@@

  }

@@

  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \textbf{} & \textbf{Yield} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}} & \textbf{Average Price} & \textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}} \\ \midrule
          Yield & 1.00 & 0.75 & 0.00 & 0.72 & 0.35 & 0.40 & -0.23 \\
          Area Harvested & 0.75 & 1.00 & -0.01 & 0.88 & 0.09 & 0.86 & -0.13 \\
          Water Used & 0.00 & -0.01 & 1.00 & 0.00 & -0.01 & 0.05 & -0.03 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.72 & 0.88 & 0.00 & 1.00 & 0.10 & 0.75 & -0.10 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.35 & 0.09 & -0.01 & 0.10 & 1.00 & -0.09 & -0.48 \\
          Average Price & 0.40 & 0.86 & 0.05 & 0.75 & -0.09 & 1.00 & 0.07 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.23 & -0.13 & -0.03 & -0.10 & -0.48 & 0.07 & 1.00 \\ \bottomrule
}
Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. 
All relationships were found to be statistically significant (P $<$ 2.200E-16).

@@

\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ Yield\end{tabular}} & 9.072E-01 & 9.061E-01 & 7.753E+02 & 2.200e-16 & 3.065E-01 & 4.913E+02 & 1.000E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ Yield/Area\end{tabular}} & 7.951E-01 & 7.770E-01 & 4.403E+01 & 2.200e-16 & 4.722E-01 & 1.085E+03 & 2.200E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ Value\end{tabular}} & 9.753E-01 & 9.748E-01 & 1.885E+03 & 2.200e-16 & 1.589E-01 & 7.111E+01 & 3.000E-02 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ Value / Area\end{tabular}} & 9.669E-01 & 9.638E-01 & 3.095E+02 & 2.200e-16 & 1.904E-01 & 9.528E+01 & 4.000E-02 \\ \bottomrule
          \end{tabular}
        }
\end{table}
Each model showed a strong relationship between the predictors and the response (see Table~\ref{tab:modelsummary}).

Aside from 3 variables, F-tests across each model indicated a good model fit. The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.36), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model; especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}).

A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See Kerries notes regarding these.
%
%For Models 1 (yield) and 3 (value) year played a pivotal role, with only one year in each model not being significant (2021/2022 and 2016/2017 respectively). Both Model 1 and 3 showed a majority of regions were significant with 32 of 54 regions being significant in Model 1, and 42 of 50 regions being significant in Model 3 at 95\% confidence.
%\newline
%\newline
%The number of combinations of year and region meant that Models 2 and 4 had many tests (424 and 243 respectively). Model 2 found 62.56\% of these combinations were indicative of a significant contribution to the model at 95\% significance. Model 4 was found to have 88.07\% of its year/region combinations indicating a significant contribution. A likely reason for some combinations not being significant was a lack of samples in that particular region/year being present; with region sample sizes ranging from 1 to 1006.
%\newline
%\newline
%With regard to continuous variables: Model 1 and 2 showed all variables to be significant at 95\% confidence when accounting for other variables. T-tests for Model 3 showed all continuous variables except scope one emissions were significant. Model 4 showed all variables aside from scope one emissions and water use to be significant; with scope one emissions and water use only being significant when considered as an interaction with area harvested but not when considered on their own.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[]
  \caption{Summary of each Models coefficients for continuous variables}\label{tab:contvar}
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}cllllll@{}}
  \toprule
    & \textbf{Intercept} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ Water\\ Used\end{tabular}}} \\ \midrule
  \textbf{Model 1} & -3.318E-02 & 7.418E-01 & 8.660E-02 & 6.731E-02 &  &  \\
  \textbf{Model 2} & -6.516E-01 & 5.774E-01 & 1.079E-02 & 8.498E-02 & -4.971E-02 & -5.346E-02 \\
  \textbf{Model 3} & 1.808E-02 & 9.713E-01 & -2.310E-02 & -6.992E-03 &  &  \\
  \textbf{Model 4} & 6.702E-01 & -7.354E-01 & -6.732E-03 & -5.645E-03 & 2.726E-02 & 7.515E-02 \\ \bottomrule
\end{tabular}}
\end{table}

@@

% Search for where you mention quality and where you mention value as this does become misleading!!!
%
% This is partly because of the intercept
%
% It depends what else is in the model.
%
% This direct comparisons are 
%
% The correlated between input vars needs to be discussed earlier.
%
%difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested had the opposite sign (see Table \ref{tab:contvar}). These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 
%
% The resource input is different by an order of magnitude between value and yield
%
% Area has the strongest nfluence
%
% The models as a ratio of area show opposite trends - this could be indicative that smaller vineyards tend twoards more valuable crops and larger to crops of greater yield. 
%
\begin{figure}
  \includegraphics{violinplot.pdf}
  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}
  \end{figure}
%

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value.pdf}}
  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value}
\end{figure}
%
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value_by_area.pdf}}
    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value_area}
\end{figure}
%
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of regional average yield and value per hectare.}\label{fig:map}
\end{figure}
%
% KM: Are these observed or modelled values?
%
% Replace with star charts?
%
%Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends. However, with area coming into play in Figure \ref{fig:yield_vs_value_area}, many data points are scaled differently; specifically the vineyards from 'Hot' regions change to be found the bottom right tail end, indicating the production of large quantity of lower value grapes. An inconspicuous difference between the Figures, is that a large amount of the difference can be explained by rotation (being $90^\circ$ clockwise from Figure \ref{fig:yield_vs_value} to \ref{fig:yield_vs_value_area}). This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}.

>>>>

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A\\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\
        \\ \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope One Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
        \\
        \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
     \textbf{Model 5} &  Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year * Region\end{tabular}
        \end{tabular}}
\end{table}

@@

Predictor variables used in this analysis included yield, defined as the total tonnes of grapes harvested, and quality, defined as average sale price of grapes. It is acknowledged that quality can be defined in a variety of ways, for example by the grapes': aroma, chemical composition and color \citep{kasimatiPredictingGrapeSugar2022,mejeanperrotDecisionsupportSystemPredict2022,suarezAssessingWineGrape2021}. Using sale price was based on the reliance of market value of winegrapes on grape quality and because Wine Australia explicitly defines grape quality through the use of discrete price brackets in their annual reports. The generalisation made to reflect quality through using average price assumed a due diligence of those who purchased the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

Missing values were improved using regional average prices from Wine Australia. Two subsets of data were then created for the analysis. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table \ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for three further models (Models 3, 4 and 5, see Table \ref{tab:tab1}. These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table \ref{tab:tab1}), where every sample had a recorded value for yield but not average price of sale per tonne.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of vineyard average income for each of the used GI Regions.}\label{fig:map}
\end{figure}%%

@@

\subsection{Exploratory Analysis}\label{sec:exp_anal}
 Table \ref{tab:summary} shows the summary statistics of each variable in its original units. The range of these values shows the level of difference between some vineyards, with operations differing by orders of magnitude in size, yield and average price of sale (See Table \ref{tab:tab1}).

@@

      % \resizebox{\textwidth}{!}{

@@

          {Yield (tonnes)} & 7.757E+02 & 2.179E+03 & 1.000E+00 & 7.231E+04 \\

@@

          {Area Harvested ($m^2$)} & 6.670E+05 & 1.337E+06 & 7.000E+02 & 2.436E+07 \\

@@

          {Water Used (ML)} & 7.471E+06 & 5.646E+08 & 1.000E+00 & 4.268E+10 \\

@@

          {Scope One Emissions ($tCO_{2}e$)} & 4.173E+04 & 8.571E+04 & 6.755E+00 & 2.110E+06 \\

@@

          $\mbox{Yield (tonnes)}\over \mbox{Area (m}^2)$ & 1.009E+01 & 8.127E+00 & 4.000E-02 & 8.634E+01 \\

@@

          {Average Sale Price (AUD)} & 1.477E+03 & 9.216E+02 & 1.600E+02 & 2.600E+04 \\

@@

          $\mbox{Average Sale Price (AUD)} \over \mbox{Area Harvested (m}^2)$ & 1.347E+02 & 5.711E+02 & 1.753E-01 & 2.979E+04 \\ \bottomrule

@@

  % }

@@

Pearson Correlation Coefficients of the transformed, centered and scaled variables are shown in Table \ref{tab:pearson_correlation}. All correlations were found to be statistically significant (P $<$ 2.200E-16). Except for 'average price' all variables are positively correlated. It can be considered that more resources and area are likely to lead to greater yields. However, the negative correlation between resource use and average sale price, although not as strong, indicates the possibility that resource consumption alone is not determining factor for grape quality.
\par
\begin{table}[]
  \caption{Pairwise Pearson correlation coefficients for logarithmically transformed values.}\label{tab:pearson_correlation}
      \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}cccccccc@{}}
          \toprule
          \textbf{} & \multicolumn{1}{c}{\textbf{Yield}} & \multicolumn{1}{c}{\textbf{Area Harvested}} & \multicolumn{1}{c}{\textbf{Water Used}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular}}} & \multicolumn{1}{c}{\textbf{Average Price}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular}}} \\ \midrule
          Yield & 1.00 & 0.88 & 0.82 & 0.76 & 0.96 & -0.46 & -0.88 \\
          Area Harvested & 0.88 & 1.00 & 0.78 & 0.83 & 0.73 & -0.19 & -0.81 \\
          Water Used & 0.82 & 0.78 & 1.00 & 0.67 & 0.76 & -0.49 & -0.82 \\
          \begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular} & 0.76 & 0.83 & 0.67 & 1.00 & 0.65 & -0.16 & -0.67 \\
          \begin{tabular}[c]{@{}c@{}}Yield by\\ Area\end{tabular} & 0.96 & 0.73 & 0.76 & 0.65 & 1.00 & -0.54 & -0.84 \\
          Average Price & -0.46 & -0.19 & -0.49 & -0.16 & -0.54 & 1.00 & 0.72 \\
          \begin{tabular}[c]{@{}c@{}}Average Price\\ by Area\end{tabular} & -0.88 & -0.81 & -0.82 & -0.67 & -0.84 & 0.72 & 1.00 \\ \bottomrule
          \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that a most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}). The models were were found to be a good fit, with overall F-tests being statistically significant (P $<$ 2.200E-16). And, aside from 3 variables, F-tests across each model's variables were also significant (with all being at least, P $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.0.39), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5); especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 9.072E-01 & 9.061E-01 & 7.753E+02 & 2.200e-16 & 3.065E-01 & 4.913E+02 & 1.000E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 7.951E-01 & 7.770E-01 & 4.403E+01 & 2.200e-16 & 4.722E-01 & 1.085E+03 & 2.200E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} & 9.753E-01 & 9.748E-01 & 1.885E+03 & 2.200e-16 & 1.589E-01 & 7.111E+01 & 3.000E-02 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 9.669E-01 & 9.638E-01 & 3.095E+02 & 2.200e-16 & 1.904E-01 & 9.528E+01 & 4.000E-02 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

Models' continuous variable's coefficient values are summarised in Table \ref{tab:contvar}. Model 1 showed all coefficients except for the intercept were significantly contributing to the model (P < 0.05). Model 2's coefficients were all statistically significant. However, for Models 3, 4 and 5 Scope one emissions did not significantly contribute. And, Model 4 only saw statistically significant contributions from the intercept and water use. Although the coefficient for water use was statistically significant for each model, it did not have the highest value, instead area harvested, being an order of magnitude greater dominated the models. Model 5 was able to achieve a similar $R^2$ to Model 4 without area harvested, having stronger influences from water use and scope one emissions.

\begin{table}[]
  \caption{Summary of each Models coefficients for continuous variables}\label{tab:contvar}
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}cllllll@{}}
  \toprule
    & \textbf{Intercept} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ scope one\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ $\ast$\\ Water\\ Used\end{tabular}}} \\ \midrule
  \textbf{Model 1} & -3.318E-02 & 7.418E-01 & 8.660E-02 & 6.731E-02 &  &  \\
  \textbf{Model 2} & -6.516E-01 & 5.774E-01 & 1.079E-02 & 8.498E-02 & -4.971E-02 & -5.346E-02 \\
  \textbf{Model 3} & 1.808E-02 & 9.713E-01 & -2.310E-02 & -6.992E-03 &  &  \\
  \textbf{Model 4} & 6.702E-01 & -7.354E-01 & -6.732E-03 & -5.645E-03 & 2.726E-02 & 7.515E-02 \\
  \textbf{Model 5} & 1.2008636941 &  & -0.040359875 & -0.017057894 &  &  \\
   \bottomrule
\end{tabular}}
\end{table}

@@

\begin{figure}
  \includegraphics{violinplot.pdf}
  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}
  \end{figure}

% Search for where you mention quality and where you mention value as this does become misleading!!!
%
% This is partly because of the intercept
%
% It depends what else is in the model.
%
% This direct comparisons are 
%
% The correlated between input vars needs to be discussed earlier.
%
%difference between the continuous variables coefficients is the change from positive to negative values. This change occurs between the Models for Yield (Model 1 and 2) and the Models for value (Models 3 and 4); where all but the coefficient for area harvested had the opposite sign (see Table \ref{tab:contvar}). These models also differ in an order of magnitude when looking at resource use, with the coefficients for yield being smaller than those for value. 
%
% The resource input is different by an order of magnitude between value and yield
%
% Area has the strongest nfluence
%
% The models as a ratio of area show opposite trends - this could be indicative that smaller vineyards tend twoards more valuable crops and larger to crops of greater yield. 
%

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value.pdf}}
  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value}
\end{figure}
%
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value_by_area.pdf}}
    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value_area}
\end{figure}
%

%
% KM: Are these observed or modelled values?
%
% Replace with star charts?
%
%Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends. However, with area coming into play in Figure \ref{fig:yield_vs_value_area}, many data points are scaled differently; specifically the vineyards from 'Hot' regions change to be found the bottom right tail end, indicating the production of large quantity of lower value grapes. An inconspicuous difference between the Figures, is that a large amount of the difference can be explained by rotation (being $90^\circ$ clockwise from Figure \ref{fig:yield_vs_value} to \ref{fig:yield_vs_value_area}). This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}.
